Evaluating Cloud-Optimized HDF5 for NASA’s ICESat-2 Mission

### 2025-01-16 paper.qmd
Fix title
add "archived in"
remove unnecessary qualification

## Problem

Scientific data from NASA and other agencies are increasingly being distributed from the commercial cloud. Cloud storage enables large-scale workflows and should reduce local storage costs. It also allows the use of scalable on-demand cloud computing resources by individual scientists and the broader scientific community. However, the majority of this scientific data is stored in a format that was not designed for the cloud: The Hierarchical Data format or HDF.

>>>>

## The Problem

Scientific data from NASA and other agencies are increasingly being archived in and distributed from the commercial cloud. Cloud storage enables large-scale workflows and should reduce local storage costs. It also allows the use of scalable on-demand cloud computing resources. However, the majority of this scientific data is stored in a format that was not designed for the cloud: The Hierarchical Data format or HDF.
